Exceedance probability comparison for the simplified Naomi model

### 2023-06-18 src/naomi-simple_exceedance/exceedance.Rmd
Add RMSE and MAE to exceedance plot

```{r}
df_wide <- bind_rows(
  df_wide_second90 %>%
    mutate(type = "Second 90"),
  df_wide_1inc %>%
    mutate(type = "High incidence")
)

write_csv(df_wide, "exceedance.csv")

@@

exceedance_manuscript_plot <- df_wide %>%
  pivot_longer(cols = c("TMB", "aghq"), names_to = "method", values_to = "estimate") %>%
  mutate(
    method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq"),
    type = fct_relevel(type, "Second 90", "High incidence")
  ) %>%
  ggplot(aes(x = tmbstan, y = estimate, col = sex)) +
    geom_point(shape = 1, alpha = 0.6) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#56B4E9", "#999999"), labels = c("Female", "Male")) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    facet_grid(type ~ method) +
    labs(x = "", y = "", col = "Sex") +
    theme_minimal() +
    theme(
      legend.position = "bottom"
    )

exceedance_manuscript_plot

>>>>

```{r}
df_wide <- bind_rows(
  df_wide_second90 %>%
    mutate(indicator = "Second 90"),
  df_wide_1inc %>%
    mutate(indicator = "High incidence")
)

@@

df_metrics <- df_wide %>%
  select(TMB, aghq, truth = tmbstan, indicator) %>%
  pivot_longer(
    cols = c("TMB", "aghq"),
    names_to = "method",
    values_to = "approximate"
  ) %>%
  group_by(indicator, method) %>%
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) %>%
  mutate(method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq"))

df_metrics_pct <- df_metrics %>%
  ungroup() %>%
  group_by(indicator) %>%
  summarise(
    rmse_diff = 100 * (min(rmse) - max(rmse)) / max(rmse),
    mae_diff = 100 * (min(mae) - max(mae)) / max(mae)
  )

df_metrics <- df_metrics %>%
  left_join(
    mutate(df_metrics_pct, method = "PCA-AGHQ"),
    by = c("indicator", "method")
  ) %>%
  mutate(
    label = ifelse(
      method == "PCA-AGHQ",
      paste0("RMSE: ", signif(rmse, 2), " (", signif(rmse_diff, 2), "%)", "\nMAE: ", signif(mae, 2), " (", signif(mae_diff, 2), "%)"),
      paste0("RMSE: ", signif(rmse, 2), "\nMAE: ", signif(mae, 2))
    )
  ) %>%
  ungroup()

write_csv(df_metrics, "exceedance.csv")

exceedance_manuscript_plot <- df_wide %>%
  pivot_longer(cols = c("TMB", "aghq"), names_to = "method", values_to = "estimate") %>%
  mutate(
    method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq"),
    indicator = fct_relevel(indicator, "Second 90", "High incidence")
  ) %>%
  ggplot(aes(x = tmbstan, y = estimate)) +
    geom_point(aes(col = sex), shape = 1, alpha = 0.6) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#56B4E9", "#999999"), labels = c("Female", "Male")) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    facet_grid(indicator ~ method) +
    labs(x = "NUTS", y = "", col = "Sex") +
    theme_minimal() +
    theme(
      legend.position = "bottom"
    )

exceedance_manuscript_plot <- exceedance_manuscript_plot +
  geom_text(
    data = df_metrics %>% mutate(method = fct_relevel(method, "TMB", "PCA-AGHQ")),
    aes(x = -Inf, y = Inf, label = label),
    size = 3, hjust = 0, vjust = 1.5
  )
